A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-22 tex/codatadp.tex
more

If there exists a closed derivation tree with root node $\Ec$, we conclude that $\Ec$ is $\thD$-unsatisfiable.
And if there exists a derivation tree with root node $\Ec$ that contains a saturated node, we conclude that $\Ec$ is $\thD$-satisfiable.

>>>>

Correctness means that if there exists a closed derivation tree with root node
$\Ec$, we can conclude that $\Ec$ is $\thD$-unsatisfiable; and if there exists
a derivation tree with root node $\Ec$ that contains a saturated node, we can
conclude that $\Ec$ is $\thD$-satisfiable.
